Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-08-01 paper.tex
Add more citations

We will also use faster resonating actuators and high-speed
camera systems to track material deformations at high frame rates. Furthermore, we plan to track
the whole material volume rather than the outer material surface. This is possible since we can
print materials in clear color as well. Thus small color-coded markers can be easily embedded into
the material structure. These markers can be tracked in 3D using a multi-camera system.
\subsection{Optimization for Fabrication}
Caustics, shadowpix, balloon
\section{System Description}
The software framework (shown in Figure~\ref{fig:framework}) is composed of 
a set of software
modules that can be easily modified or exchanged. The first component
of this framework is an output-device-independent description API
that allows the user to specify any physical object in terms of its physical
properties such as geometry, mechanical behaviors, and appearance. 
The framework will also provide physically-based
simulation tools that accurately predict the behavior of our output device.
The goal of the optimization module is to search through
the space of possible device outputs and deliver one that best matches the
desired model. In order to evaluate the quality of the match between the
simulation output and the desired model we need to develop appropriate
comparison metrics. Finally, a central component of our framework is
a reduction model which makes the optimization problem tractable by
reducing the search space as much as possible.
The reduction model can specified by experts or deduced from a
set of examples. Next, we will describe each element of the framework in
more detail.
\begin{figure}
\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
\caption{API overview. The diagram will become nicer.}
\label{fig:framework}
\end{figure}
\subsection{Input API}
Our input API handles three tasks: specifying an optimization problem,
maintaining a material library and configuring existing modules of
the optimization process.
An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}

>>>>

We will also use faster resonating actuators and high-speed
camera systems to track material deformations at high frame rates. Furthermore, we plan to track
the whole material volume rather than the outer material surface. This is possible since we can
print materials in clear color as well. Thus small color-coded markers can be easily embedded into
the material structure. These markers can be tracked in 3D using a multi-camera system.
\subsection{Optimization for Fabrication}
\cite{Finckh:2010} computing surface height field
of transparent material to match caustics pattern.
ShadowPix \cite{Bermano:2012} produced surface geometry
that produces different images 
under different lighting
directions. \cite{sko:2012} produced balloons that match 3D models when
inflated.
\section{System Description}
The software framework (shown in Figure~\ref{fig:framework}) is composed of 
a set of software
modules that can be easily modified or exchanged. The first component
of this framework is an output-device-independent description API
that allows the user to specify any physical object in terms of its physical
properties such as geometry, mechanical behaviors, and appearance. 
The framework will also provide physically-based
simulation tools that accurately predict the behavior of our output device.
The goal of the optimization module is to search through
the space of possible device outputs and deliver one that best matches the
desired model. In order to evaluate the quality of the match between the
simulation output and the desired model we need to develop appropriate
comparison metrics. Finally, a central component of our framework is
a reduction model which makes the optimization problem tractable by
reducing the search space as much as possible.
The reduction model can specified by experts or deduced from a
set of examples. Next, we will describe each element of the framework in
more detail.
\begin{figure}
\includegraphics[width=0.45\textwidth]{figure/framework.pdf}
\caption{API overview. The diagram will become nicer.}
\label{fig:framework}
\end{figure}
\subsection{Input API}
Our input API handles three tasks: specifying an optimization problem,
maintaining a material library and configuring existing modules of
the optimization process.
An overview of the three components of our API is shown in Figure~\ref{fig:inputAPI}
